Modeling the Linux page cache for accurate simulation of data-intensive applications

### 2021-05-21 paper_io_sim.tex
New average errors

    \begin{figure*}
        \centering
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=\linewidth]{result/single/figures/single_errors_v2.pdf}
               \vspace*{-0.7cm}
               \caption{Relative simulation errors (absolute values)\\ Left: 20-GB files. Right: 100-GB files.}
                \vspace*{0.2cm}
               \label{fig:single_error}
            \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
            %    Gray shades represent task phases (read, compute and write).
            %    Lines represent memory usage along pipeline execution time.}
               \includegraphics[width=\linewidth]{result/single/figures/single_memprof_v2.pdf}
               \vspace*{-0.7cm}
               \caption{Memory profiles\\ From top to bottom: real execution, Python prototype, WRENCH cache. Left: 20-GB files. Right: 100-GB files.}
               \vspace*{0.2cm}
               \label{fig:single_memprof}
        \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=\linewidth]{result/single/figures/cached_files_v2.pdf}
               \caption{Page cache content after each I/O operation\\Left: 20-GB files. Right: 100-GB files.}
            %    \textcolor{red}{Update real results of 20GB}}
               \label{fig:single_cache}
        \end{subfigure}
        \caption{Single-threaded results (\textit{Exp 1})}
        \end{figure*}

@@

        The page cache simulation model drastically reduces I/O simulation
        errors in each application task (Figure~\ref{fig:single_error}). Errors were reduced from an average
        of 345\% in the original \wrench to 46\% in the Python prototype and
        39\% in \wrench-cache. Unsurprisingly, the original \wrench simulator
        significantly overestimated read and write times, due to the lack
        of page cache simulation. Consistently, the first read was not impacted
        as it only involved uncached data. Results with files of 50~GB and 75~GB
        showed similar behaviors and are not reported for brevity.

>>>>

    \begin{figure*}
        \centering
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=\linewidth]{result/single/figures/single_errors.pdf}
               \vspace*{-0.7cm}
               \caption{Relative simulation errors (absolute values)\\ Left: 20-GB files. Right: 100-GB files.}
                \vspace*{0.2cm}
               \label{fig:single_error}
            \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
            %    Gray shades represent task phases (read, compute and write).
            %    Lines represent memory usage along pipeline execution time.}
               \includegraphics[width=\linewidth]{result/single/figures/single_memprof.pdf}
               \vspace*{-0.7cm}
               \caption{Memory profiles\\ From top to bottom: real execution, Python prototype, WRENCH cache. Left: 20-GB files. Right: 100-GB files.}
               \vspace*{0.2cm}
               \label{fig:single_memprof}
        \end{subfigure}
        \begin{subfigure}{\linewidth}
            \centering
               \includegraphics[width=\linewidth]{result/single/figures/cached_files.pdf}
               \caption{Page cache content after each I/O operation\\Left: 20-GB files. Right: 100-GB files.}
            %    \textcolor{red}{Update real results of 20GB}}
               \label{fig:single_cache}
        \end{subfigure}
        \caption{Single-threaded results (\textit{Exp 1})}
        \end{figure*}

@@

        The page cache simulation model drastically reduces I/O simulation
        errors in each application task (Figure~\ref{fig:single_error}). Errors were reduced from an average
        of 328\% in the original \wrench to 36\% in the Python prototype and
        32\% in \wrench-cache. Unsurprisingly, the original \wrench simulator
        significantly overestimated read and write times, due to the lack
        of page cache simulation. Consistently, the first read was not impacted
        as it only involved uncached data. Results with files of 50~GB and 75~GB
        showed similar behaviors and are not reported for brevity.
